%------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------
\newcommand*{\TEXPATH}{classes/}
\documentclass[11pt, a4paper]{\TEXPATH awesome-cv} 
\usepackage[english]{babel}

% Configure page margins with geometry
\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} 
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-emerald} % Default colors include: awesome-emerald,
%awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis,
%awesome-concrete, awesome-darknight

% Uncomment if you would like to specify your own color
%\definecolor{awesome}{HTML}{CA63A8}

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

% If you would like to change the social information separator from a pipe (|)
%to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} 

%---------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%---------------------------------------------------------------------

\name{Antonio}{Salvucci}
\dob{Latina (IT) on July 13th, 1983}
\mobile{(+39) 327-76-99-320}
\email{s4lb04@gmail.com}
\gitlab{salvucci}
\googleScholar{https://scholar.google.it/citations?user=xhzjY6kAAAAJ\&hl=en}
\orcid{https://orcid.org/0000-0003-4876-2613}
\linkedin{antonio-salvucci}
\skype{s4lb04}
\address{Address: Chemin de la Ramaz, 116 - 01630 Sergy (FR)}
\position{Physics Ph.D.}

%---------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%---------------------------------------------------------------------

%The company being applied to
\recipient{SOPHiA GENETICS}{
  \vspace{-0.6em}Rue du Centre 172, Saint Sulpice (CH)}
% The date on the letter, default is the date of compilation
\letterdate{Sergy, \monthyeardate\today}

%Letter Title
\lettertitle{Job Application for C++ Software Developer
  (\href{https://jobs.lusk.io/sophia-genetics-sa/c-software-developer-interested-in-genomics-applications-lausanne-switzerland-3f514ea0}{\textbf{\color{awesome!40!gray}{JobRef}}})
}

% How the letter is opened
\letteropening{Dear Hiring Manager,}

% How the letter is closed
\letterclosing{Sincerely,} 

%\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

% Specify the letter footer with 3 arguments: (<left>, <center>, <right>),
% leave any of these blank if they are not needed
\makecvfooter{\monthyeardate\today}{Antonio Salvucci~~~·~~~Cover Letter}{} 
  
%-------------------------------------------------------------------------

\begin{document}
\makecvheader % Print the header
\makelettertitle % Print the title

%------------------------------------------------------------------------
%	LETTER CONTENT
%------------------------------------------------------------------------

\begin{cvletter}

  I am writing to express my interest in the C++ Software Developer position at
  your company (St. Sulpice headquarter). I learned about your company through
  the LinkedIn social network, and after visiting your website, I have immersed
  myself in your groundbreaking work in the data analytics solutions to support
  healthcare professionals.

  I am a physicist by education, with a strong passion for software programming
  and information technology. For almost a decade, I have been working as
  researcher in the field of particle physics within the international
  collaboration of the ATLAS Experiment at CERN. I am now looking to transition
  in the private sector to grow as a professional and contribute more directly
  to social wealth. I matured solid skills as both software developer and data
  analyst:
  \begin{itemize}
  \item[-] I developed software algorithms, making use of object oriented
    programming (mainly C++) and scripting languages (mainly Python). I
    designed my algorithms both for parallel and for distributed systems;
  \item[-] I analysed a large amount of data (50 PB/year produced by the
    CERN LHC) and extracted meaning from they by using statistical tools and
    machine learning techniques;
  \item[-] I am an advanced Linux user with system administration know-how and
    proficient bash scripting skills;
  \item[-] I am an effective debugger and optimiser, and I am adept at
    implementing strategic workflows to run functional tests for performance
    improvement.
  \end{itemize}
  I invite you to take a look at my public gitlab profile
  (gitlab.cern.ch/salvucci).
  
  I have a solid academic foundation and a strong passion for boosting
  innovation through information technology and data analysis. I am thrilled by
  the opportunity of measuring my technical knowledge in the application fields
  of bio-informatics and genomics. I am an enthusiastic team-player as well as
  an hard-worker, who sees opportunities into challenges.
  
  I am confident my expertise in software programming and data analysis, as well
  as my mindset and genuine interest, make me a great candidate for this
  opening. I would much appreciate the opportunity to contribute to your
  ongoing growth and continued success.

  I would be delighted to meet you in person at your earliest convenience.
  I look forward to discussing this position in more details and sharing more
  about myself and previous experience.

  Should you have any question or need further further information, please do
  not hesitate to contact me.

  Thank you for your consideration.
  
\end{cvletter}
 
%----------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}
