%------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%------------------------------------------------------------------------
\newcommand*{\TEXPATH}{classes/}
\documentclass[11pt, a4paper]{\TEXPATH awesome-cv} 
\usepackage[british]{babel}

% Configure page margins with geometry
\geometry{left=2cm, top=1.5cm, right=2cm, bottom=2cm, footskip=.5cm} 
 
\fontdir[fonts/] % Specify the location of the included fonts

% Color for highlights
\colorlet{awesome}{awesome-emerald} % Default colors include: awesome-emerald,
%awesome-skyblue, awesome-red, awesome-pink, awesome-orange, awesome-nephritis,
%awesome-concrete, awesome-darknight

% Uncomment if you would like to specify your own color
%\definecolor{awesome}{HTML}{CA63A8}

% Colors for text - uncomment and modify
%\definecolor{darktext}{HTML}{414141}
%\definecolor{text}{HTML}{414141}
%\definecolor{graytext}{HTML}{414141}
%\definecolor{lighttext}{HTML}{414141}

% If you would like to change the social information separator from a pipe (|)
%to something else
\renewcommand{\acvHeaderSocialSep}{\quad\textbar\quad} 

%---------------------------------------------------------------------
%	PERSONAL INFORMATION
%	Comment any of the lines below if they are not required
%---------------------------------------------------------------------

\name{Antonio}{Salvucci}
\dob{Latina (IT) on July 13th, 1983}
\mobile{(+39) 327-76-99-320}
\email{s4lb04@gmail.com}
\gitlab{salvucci}
\googleScholar{https://scholar.google.it/citations?user=xhzjY6kAAAAJ\&hl=en}
\orcid{https://orcid.org/0000-0003-4876-2613}
\linkedin{antonio-salvucci}
\skype{s4lb04}
\address{Address: Chemin de la Ramaz, 116 - 01630 Sergy (FR)}
\position{Physics Ph.D.}

%---------------------------------------------------------------------
%	RECIPIENT/POSITION/LETTER INFORMATION
%	All of the below lines must be filled out
%---------------------------------------------------------------------

%The company receiving the letter
\recipient{Radboud University}{
  \vspace{-0.6em}Nijemgen (NL)}
% The date on the letter, default is the date of compilation
\letterdate{\monthyeardate\today}

%Letter Title
%\lettertitle{Job Application for Postdoctoral Researcher in experimental
%  particle physics - ATLAS
%  (\href{https://www.nikhef.nl/en/vacancies/}{\textbf{\color{awesome!40!gray}{JobRef}}})
%}

% How the letter is opened
\letteropening{Dear Dean of the Faculty of Science,}


% How the letter is closed
\letterclosing{Sincerely,} 

%\letterenclosure[Attached]{Curriculum Vitae} % Any enclosures with the letter

% Specify the letter footer with 3 arguments: (<left>, <center>, <right>),
% leave any of these blank if they are not needed
\makecvfooter{\monthyeardate\today}{Antonio Salvucci}{} 
  
%-------------------------------------------------------------------------

\begin{document}
\makecvheader % Print the header
\makelettertitle % Print the title

%------------------------------------------------------------------------
%	LETTER CONTENT
%------------------------------------------------------------------------

\begin{cvletter}
  
  It is a pleasure to introduce myself. My name is Antonio Salvucci, and I am
  writing this letter to grant full promotion rights to Dr. Frank Filthaut at
  the role of Professor at the Radboud University of Nijmegen.

  Since 2008, I am a member of the ATLAS collaboration - one of the four
  experiments installed along the perimeter of the Large Hadron Collider
  (LHC) at CERN. Within this context, I got my Master of Science degree in
  physics at the Universit\`a degli Studi di Roma ``Tor Vergata'' (in Rome,
  Italy) in September 2010. Few months later, in February 2011, I started my
  PhD in high-energy physics at the Radboud University of Nijmegen, obtaining
  my doctoral degree (cum laude) in September 2014. I am currently finalising
  the third year of my postodoctoral experience at the Chinese University of
  Hong Kong.

  The doctoral experience I matured at the Radboud University under the
  supervision of Frank played a key role in shaping my career as particle
  physicist at CERN. Frank guided me in choosing the main topic of my PhD
  thesis, which was the search for the Standard Model (SM) Higgs boson and
  the measurement of its properties. Frank demonstrated to be extremely able
  to visualize the big picture, and to entrust his team to achieve excellent
  goals. His guidance let myself, and ultimately the Radboud University, to
  be key in the discovery of the Higgs boson, which let to the Nobel Prize in
  physics in 2013.

  Frank is an excellent strategic thinker, as he well demonstrated during our
  period of collaboration. As I was involved in the search for the SM Higgs
  boson in the decay channel with four muons, Frank suggested to dedicate
  part of my research time in the study of the performance of the ATLAS
  tracking system. His suggestion was extremely valuable not only for my
  professional development, but also for the contribution made to the whole
  ATLAS experiment, and ultimately to the scientific community. The PhD
  training with Frank allowed me to become an expert in the functioning of
  the ATLAS tracking system, and made myself a profile of reference in the
  whole collaboration.
  
  As from the educational point of view, Frank demonstrated to have natural
  skills of educator. I do not recall a single occasion in which I needed
  help and I did not find his support. His physics knowledge is remarkable
  and broad - I still remember our fruitful discussions concerning physics,
  data analysis, statistics, computer programming, and detector functioning.
  On a different, but extremely crucial note, Frank is one of the most humble
  scientist I have ever met. While working with him, I never felt myself to
  be a simple PhD student, but rather a scientist whose opinion and knowledge
  was worth to be taken into account. He has the talent of empowering young
  researchers, transfer knowledge, and build confidence.
  
  Frank was a mentor, rather than a supervisor. While giving myself the
  freedom to express my capabilities at best, he has been always a trustable
  presence behind my shoulders - not only from a professional point of view,
  but also as a human being.
  
  To conclude, I strongly encourage you to grant full promotion rights to Frank
  at the role of Professor. I believe he will be remarkably valuable to shape
  the careers of the next generations of scientists and increase the impact of
  the Radboud University within the international scientific community.
  
\end{cvletter}

%----------------------------------------------------------------------------

\makeletterclosing % Print the signature and enclosures

\end{document}
