%-----------------------------------------------------------------------
%	SECTION TITLE
%-----------------------------------------------------------------------
\cvsection{{Responsibilities in ATLAS}}

%-----------------------------------------------------------------------
%	SECTION CONTENT
%-----------------------------------------------------------------------
\begin{cvinterests}

%------------------------------------------------

\cvinterest{
%
\textbf{Higgs and Physics/Modelling group}\\
\vspace{-2em}
\begin{itemize}[labelwidth=0.05in,align=right,leftmargin=!,labelsep=0pt,
itemsep=0.0em]
\item[] \textsc{\color{awesome}{Higgs MC production manager}} (since Nov. 2016).
Responsible for Monte Carlo production, validation and submission on behalf of
the Higgs group (obtaining Class 3 OTP credits).
\end{itemize}
%
\textbf{Higgs HZZ group}\\
\vspace{-2em}
\begin{itemize}[labelwidth=0.05in,align=right,leftmargin=!,labelsep=0pt,
itemsep=0.0em]
\item[] \textsc{\color{awesome}{analysis contact}} (since Jul. 2018) for the
measurement of the fiducial and differential cross sections measurements;
\item[] \textsc{\color{awesome}{editor}} (Oct. 2017 - Jun. 2018) of the
supporting documentation for CONF note (\href{https://atlas.web.cern.ch/Atlas/GROUPS/PHYSICS/CONFNOTES/ATLAS-CONF-2018-018/}{ATLAS-CONF-2018-018})
showing the results of the Higgs boson properties measurements (fiducial and
differential cross sections and couplings) in the context of the $4\ell$ decay
channel using \SI{80}{\per\femto\barn} of $pp$ collision data at $\sqrt{s}=13$
\si{\tera\electronvolt};
\item[] \textsc{\color{awesome}{editor}} (Oct. 2016 - May 2017) of the
supporting documentation for the paper (\href{https://link.springer.com/article/10.1007/JHEP10(2017)132}{JHEP 10 (2017) 132})
and CONF note (\href{http://cdsweb.cern.ch/record/2265796}{ATLAS-CONF-2017-032})
on fiducial and differential cross sections measurements published using
\SI{36.1}{\per\femto\barn} of $pp$ collision data at
$\sqrt{s}=13$ \si{\tera\electronvolt};
\item[] \textsc{\color{awesome}{responsible}} for Monte Carlo validation (signal
and background samples) and submission between September 2012 and April 2014.
\end{itemize}
%
\textbf{Lepton+X/Exotics group}\\
\vspace{-2em}
\begin{itemize}[labelwidth=0.05in,align=right,leftmargin=!,labelsep=0pt,
itemsep=0.0em]
\item[] \textsc{\color{awesome}{analysis contact}} (since Sep. 2016) for
the search for lepton-flavor violating high-mass dilepton final states and 
\textsc{\color{awesome}{editor}} of the paper 
(\href{https://journals.aps.org/prd/abstract/10.1103/PhysRevD.98.092008}{Phys. Rev. D 98, 092008}) and corresponding supporting documentation published using
\SI{36.1}{\per\femto\barn} of $pp$ collision data at
$\sqrt{s}=13$ \si{\tera\electronvolt}.
\item[] \textsc{\color{awesome}{editor}} (Dec. 2015 - Aug. 2016) of the
paper (\href{https://link.springer.com/article/10.1140/epjc/s10052-016-4385-1}{Eur. Phys. J. C 76 (2016) 541}),
CONF note (\href{https://cds.cern.ch/record/2114844}{ATLAS-CONF-2015-072}) and
supporting documentation in the previous round of the analysis (search for
lepton-flavor violating high-mass dilepton final states) published using
\SI{3.2}{\per\femto\barn} of $pp$ collision data at
$\sqrt{s}=13$ \si{\tera\electronvolt}.
\item[] \textsc{\color{awesome}{editorial board member}} for the search for
lepton flavor violation of $Z$ boson decaying to electron and muon.
\end{itemize}
%
\textbf{Muon Combined Performance group}\\
\vspace{-2em}
\begin{itemize}[labelwidth=0.05in,align=right,leftmargin=!,labelsep=0pt,
itemsep=0.0em]
\item[] \textsc{\color{awesome}{developer and maintainer}} (Feb 2011 - Oct 2012)
of the \texttt{MuonMomentumCorrection} software package, which provides muon
resolution, smearing functions and corrections for physics analyses (obtained
Class 3 OTP credits for muon reconstruction).
\end{itemize}
%
%\textbf{Monte Carlo Simulation/Generator Software}:\\
%\vspace{-2em}
%\begin{itemize}[labelwidth=0.05in,align=right,leftmargin=!,labelsep=0pt,
%itemsep=0.0em]
%\item[] obtaining Class 3 OTP credits for Monte Carlo simulation and generation
%software (i.e. Powheg and Alpgen on-the-fly generation improvement);
%\end{itemize}
%%
}

\end{cvinterests}
